Efficiently summarising relationships in large samples: a general duality between statistics of genealogies and genomes

### 2019-09-09 treestats_paper.tex
Remove krt comment

We allow vector-valued weights,
i.e., $\iw(v)$ may be a vector $(\iw_1(v), \ldots, \iw_m(v))$,
so that when summarising we have access to more than one aspect of each subtree.
The requirement that $f(0) = f(\tiw) = 0$ is for consistency,
so that statistics do not depend on portions of the tree either not ancestral to any of the samples or ancestral to all
of them.
% Below, in section XXX, we describe how to efficiently
% maintain a list of the weights of the subtrees below each node
% as we iterate through the tree sequence.
\krt{Is this true?  If so, why isn't the current Tajima's D implentation done in one pass through the tree sequence?}
In practice we allow summary functions to be vector-valued (so as to compute many statistics at once)
but this will not feature in our examples.
Next, we will describe how to use these subtree weights,
passed through a ``summary function'' in various ways,
to summarize genetic variation and tree shapes across the tree sequence.

>>>>

We allow vector-valued weights,
i.e., $\iw(v)$ may be a vector $(\iw_1(v), \ldots, \iw_m(v))$,
so that when summarising we have access to more than one aspect of each subtree.
The requirement that $f(0) = f(\tiw) = 0$ is for consistency,
so that statistics do not depend on portions of the tree either not ancestral to any of the samples or ancestral to all
of them.
% Below, in section XXX, we describe how to efficiently
% maintain a list of the weights of the subtrees below each node
% as we iterate through the tree sequence.
